Verifying Demonstrations

### 2018-02-26 paper/RelatedWork.tex
edited and added urban count and divote

There is a body of work in the computer vision community, e.g.\ the work of 
\citet{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
algorithm on different scenes, which might make this method easier to use for 
protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
this might still be difficult.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method 
can provide a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above, i.e.\ forensic methods.

@@

A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
towers of the mobile network) to count unique phones at the location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the 
counter-protesters.
Second, since the phone is a unique identifier, participants might be 
uncomfortable to be registered in association with the event and might thus 
turn the device off.
Finally, there will be limited verifiability, as the data recorder must be 
trusted to record all data and do it in the relation to the event.

@@

The most closely related work is \citet{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

>>>>

There is a body of work in the computer vision community, e.g.\ the work of 
\citet{NNCrowdCounting}.
This class of methods requires photos or video surveillance of the protest 
location during the entire protest.
They generally include machine learning, and thus also require a training 
dataset to train the algorithms.
In the work by \citet{NNCrowdCounting}, they actually train and evaluate their 
algorithm on different scenes, which might make this method easier to use for 
protesting.
We can provide universal verifiability (\cref{UniversalVerif}) with this 
method, since someone can always recount the participants using the recorded 
video material.
We might be able to provide some degree of individual verifiability 
(\cref{IndividualVerif}), if Alice can recognize her own face in the video, but 
this might still be difficult. Automatic face recognition can help
verifiability but at the price of privacy.
Also, it is difficult (if not impossible) to not count people twice, thus we 
cannot argue for eligibility verifiability (\cref{EligibilityVerif}).
In theory, this class of methods will provide an upper bound, whereas our method 
can provide a lower bound.
However, it is still difficult to capture the entire location on surveillance 
video, which diminishes the argument for an upper bound.
The spatial and temporal verifiability properties are reduced to those of the 
video, which should be similar as in our discussion about the verifiability of 
photos above, i.e.\ forensic methods.

@@

A better proposal would be to use \enquote{IMSI catchers} (or the real cell 
towers of the mobile network) to count unique phones at the location.
However, there are several problems with this approach.
First, it will be difficult to register only the participants' phones, many 
bystanders will also be counted.
It is also difficult to differentiate between the protesters and the 
counter-protesters.
Second, since the phone is a unique identifier, participants might be 
uncomfortable to be registered in association with the event and might thus 
turn the device off, even though, at least with 5G, the IMSI will not be
transmitted in plaintext anymore. %need to cite?
Finally, there will be limited verifiability, as the data recorder must be 
trusted to record all data and do it in the relation to the event.

@@

One of the most closely related work is \citet{CrowdCount}.
This is a web service which lets Alice create an event and Bob can submit his 
location to register that he is in Alice's event.
This solves the problem that it counts everyone (who submitted), not just the 
count at the snapshot of the photos.
However, there is no verification, i.e.\ the service must be trusted to behave 
honestly, but even then, nothing prevents Bob from submitting twice (violating 
eligibility, \cref{EligibilityVerif}).
Another downside is that the service also requires an Internet connection 
during the event to register as a participant.
This can make it difficult to use if e.g.\ Alice has organized a protest 
against the government, who shuts down the cellular network or Internet 
backbone as a means to censor the protest.

Another related approach based on devices is \citet{UrbanCount} which
uses epidemic spreading of crowd-size estimates by device-to-device
communication to count crowds in dense urban environments with high
node mobility and churn. There is, however, no consideration of a potentially
adverserial setting and thus no verification or checks on
eligibility. \citet{DiVote}, a prior work by the same authors for
polling in dense areas, avoids double counting but again only for
honest participants.
